---
title: "CRT Lab3"
author: 
  - "Tess Sameshima"
  - "Chris Ives"
  - "Rachael Latimer"
date: "5/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
needs(tidyverse, palmerpenguins)
```

## Part A: Foundations
1. Briefly name and describe the three fundamental components of a function.

2. Describe three different ways functions can be stored/applied and an example of when you might want to use each version.


```{r PartA}
#Three fundamental components of a function:
#1. body(): the statements executed when the function runs
#2. formals(): the arguments supplied to the function
#3. environment(): the structure that determines how the function finds the values associated with the names

#Three ways functions can be stored/applied.
#1. A function can be stored as an object.
#2. Anonymous function (unbound to name)
#3. Stored in a list

```

## Part B: Applied practice
1. Write a function to calculate the mean that removes missing data before conducting the calculation. You may not use base::mean or any similar function that conducts a mean calculation. Include a warning in your function if missing data have been removed that prints the total number of cases that were removed.

```{r PartB1}
mn <- function(x) {
    if(sum(is.na(a)) > 0) {
    warning(sum(is.na(a)), " counts were removed due to missingness")
  }
  d <- na.omit(a)
    sum(d)/length(d)
}

```

2. Test your function to make sure it (a) provides the expected results, and (b) gives identical output to base::mean when na.rm = TRUE. Make sure that you test your data against a vector that has missing data.
```{r PartB2}
a <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, NA)

mn(a)
mean(a, na.rm = TRUE)


```
3. Turn the following three lines of code into three different functions. Make sure to give them meaningful names. Test the functions to make sure they provide the expected output.
```{r PartB3}

na_count <- function(x) {
  sum(is.na(x))
}

prop_rep <- function(x) {
  map_dbl(split(x, x), length)/length(x)
}

prop_rep(mtcars$cyl)

znorm <- function(x) {
  (x - mean(x, na.rm = T)) /
    sd(x, na.rm = T)
}
znorm(mtcars$mpg)
```
4. Write a function that takes a data frame as its input and returns a data frame with only the numeric columns.

```{r PartB4}
num_cols <- function(x) {
  sub <- map_lgl(x, is.numeric)
  x <- x[, sub]
  return(x)
  }
```
5. Write a function that uses the function you wrote in Question 5, and returns a data frame with the mean and standard deviation of each numeric column. If columns are omitted (because they are non-numeric), print a message stating the specific columns that were not included.

```{r PartB5}

col_m_sd <- function(x) {
  d <- num_cols(x)

  if(length(x) != length(d)) {
    non_nm <- names(x[, !(colnames(x)) %in% names(d)])
    warning("The following non-numeric columns were ommitted:", paste(non_nm, collapse = " "))
  }
  
  d %>% 
  pivot_longer(everything(), names_to = "var", values_to = "val") %>% 
  group_by(var) %>% 
  summarise(mean = mean(val, na.rm = TRUE),
            sd = sd(val, na.rm = TRUE))
}
  

col_m_sd(penguins)
```


