---
title: "CRT Lab3"
author: 
  - "Tess Sameshima"
  - "Chris Ives"
  - "Rachael Latimer"
date: "5/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Part A: Foundations
1. Briefly name and describe the three fundamental components of a function.

2. Describe three different ways functions can be stored/applied and an example of when you might want to use each version.


```{r PartA}
#Three fundamental components of a function:
1. 
2. 
3.  

#Three ways functions can be stored/applied.
1.
2.
3.

```

## Part B: Applied practice
1. Write a function to calculate the mean that removes missing data before conducting the calculation. You may not use base::mean or any similar function that conducts a mean calculation. Include a warning in your function if missing data have been removed that prints the total number of cases that were removed.

2. Test your function to make sure it (a) provides the expected results, and (b) gives identical output to base::mean when na.rm = TRUE. Make sure that you test your data against a vector that has missing data.

3. Turn the following three lines of code into three different functions. Make sure to give them meaningful names. Test the functions to make sure they provide the expected output.



```{r PartB_1_3}

```

4. Write a function that takes a data frame as its input and returns a data frame with only the numeric columns.

5. Write a function that uses the function you wrote in Question 5, and returns a data frame with the mean and standard deviation of each numeric column. If columns are omitted (because they are non-numeric), print a message stating the specific columns that were not included.

```{r PartB_4_5}

```

